---
title: "Buffer"
author: "Jonathan Slaney"
date: "23/02/2021"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for master's thesis buffer calculation 

## Required packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(naniar)
library(ggmap)
library(ggthemes)
library(sf)
library(rgeos)
library(cancensus)
library(cowplot)
library(ggspatial)
library(knitr)
library(lmtest)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(kableExtra)
```

## Game plan

1. SD participants
2. Simplify date
3. Summarize (makes results table of MVPA)
4. Figures
5. Visualize GPS points + bike infrastructure 2017/ 2019
6. Apply 70m buffer -> st_buffer()
7. Convert buffer file to sf.dataframe
8. Run st_intersect for buffer vs participant gps data

# Filter SD Participants

```{r}
## Reading in SD data
SD_vic_one <- read_csv("/Users/dfuller/Documents/INTERACT/data/sensors/victoria_01_top_1min_2020-01-10_sd.csv") # read in SD w1 participants n = 129
SD_vic_one <- SD_vic_one %>% mutate(sensedoc = "1") # Add variable to SD w1 (1)
SD_vic_two <- read_csv("/Users/dfuller/Documents/INTERACT/data/sensors/victoria_02_top_1min_2020-06-13_sd.csv") # read in SD w2 participants n = 153
SD_vic_two <- SD_vic_two %>% mutate(sensedoc = "2") # Add variable to victoria health w1 (1)
SD_vic_all <- bind_rows(SD_vic_one, SD_vic_two)

tabyl(SD_vic_all, interact_id, wave_id)
```

## Some basic cleaning

```{r warning=FALSE}
# Filter out if they are not in the city, Reason: No CTUID for out of the city
SD_vic_all <- SD_vic_all %>% filter(in_city == 1 & wearing == 1)

SD_vic_all <- SD_vic_all %>%
	mutate(activity_levels = case_when(
		x_count < 100 ~ "sedentary",
		x_count >= 100 & x_count <= 1951 ~ "light",
		x_count >= 1951 & x_count <= 5724 ~ "moderate",
	  x_count >= 5725 ~ "vigorous"
	))

sd_data <- SD_vic_all
```

## Create a date column and add a minutes in census tract by id, date, and census tract column

```{r}
#### SenseDoc
table(sd_data$wave_id)
sd_data$date <- sd_data$utcdate %>% as.Date()
sd_data$minutes <- 1
sd_data <- sd_data %>% 
  group_by(interact_id, date, wave_id) %>% 
  mutate(
      minutes_id_date = sum(minutes)
  )
```

### MPVA Minutes SenseDoc

```{r}
table(sd_data$activity_levels)
table(sd_data$wearing)
### MVPA Minutes
sd_data <- sd_data %>%
	mutate(mvpa = case_when(
		activity_levels == "light" ~ 0,
		activity_levels == "sedentary" ~ 0,
		activity_levels == "moderate" ~ 1,
		activity_levels == "vigorous" ~ 1
	))
### Sed Minutes
sd_data <- sd_data %>%
	mutate(sed = case_when(
		activity_levels == "light" ~ 0,
		activity_levels == "sedentary" ~ 1,
		activity_levels == "moderate" ~ 0,
		activity_levels == "vigorous" ~ 0
	))
### Sed Minutes
sd_data <- sd_data %>%
	mutate(light_pa = case_when(
		activity_levels == "light" ~ 1,
		activity_levels == "sedentary" ~ 0,
		activity_levels == "moderate" ~ 0,
		activity_levels == "vigorous" ~ 0
	))
sd_data <- sd_data %>% 
    group_by(interact_id, date) %>% 
      mutate(
        total_mvpa_minutes = sum(mvpa),
        total_sed_minutes = sum(sed),
        total_light_pa_minutes = sum(light_pa)
        )
sd_pa_table <- sd_data %>%
                group_by(interact_id, date, wave_id) %>%
                  summarise(
                    time = mean(minutes_id_date, na.rm = TRUE),
                    wearing = mean(wearing, na.rm = TRUE),
                    mean_mpva_sd = mean(total_mvpa_minutes, na.rm = TRUE), 
                    sd_mpva_sd = sd(total_mvpa_minutes, na.rm = TRUE), 
                    mean_sed_sd = mean(total_sed_minutes, na.rm = TRUE), 
                    sd_sed_sd = sd(total_sed_minutes, na.rm = TRUE), 
                    mean_light_sd = mean(total_light_pa_minutes, na.rm = TRUE), 
                    sd_light_sd = sd(total_light_pa_minutes, na.rm = TRUE), 
                    na_count = sum(is.na(total_mvpa_minutes)), 
                    count = n()
                  )
sd_pa_table
sd_sum_table <- sd_pa_table %>%
                group_by(wave_id) %>%
                  summarise(
                    time = mean(time, na.rm = TRUE), 
                    wearing = mean(wearing, na.rm = TRUE), 
                    mean_mpva_sd = mean(mean_mpva_sd, na.rm = TRUE), 
                    mean_sed_sd = mean(mean_sed_sd, na.rm = TRUE), 
                    mean_light_sd = mean(mean_light_sd, na.rm = TRUE), 
                    na_count = sum(is.na(time)), 
                    count = n()
                  )
sd_sum_table
```

### SD Activity Figures by wave

```{r}
##  formula = y ~ s(x, bs = "cs") with method = "REML".
wave1_activity <-  sd_pa_table %>% 
              filter(wave_id == "1") %>% 
              ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd),  colour = "black") +    
                  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                  ylim(0, 400) +
                  labs(x = "Date", y = "Minutes") +
                  theme_classic()
plot(wave1_activity)
ggsave("wave1_activity.jpg", dpi = 150, height = 4, width = 6)
```

```{r}
##  formula = y ~ s(x, bs = "cs") with method = "REML".
wave2_activity <-  sd_pa_table %>% 
              filter(wave_id == "2") %>% 
              ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd),  colour = "black") +    
                  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                  ylim(0, 400) +
                  labs(x = "Date", y = "Minutes") +
                  theme_classic()
plot(wave2_activity)
ggsave("wave2_activity.jpg", dpi = 150, height = 4, width = 6)
```

```{r}
victoria_activity <-  sd_pa_table %>% 
          ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd), colour = "black") +     
                scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                ylim(0, 400) +
                labs(x = "Date", y = "Minutes") +
                theme_classic()
plot(victoria_activity)
ggsave("victoria_activity.jpg", dpi = 150, height = 4, width = 6)
```

# Buffers around lanes 2017 and 2019

## Apply 70m buffer to Pandora bike lane

### Read in 2017 Shape file

```{r}
getwd()
#Note to self all file formats must be in same directory (I think it's .shp and .shx that really matter)
vic_int <- st_read("/Users/dfuller/Documents/INTERACT/data/intervention/victoria/IBIMS_2017.shp")
```

#### Plot Vic 2017 shape 
```{r}
st_crs(vic_int)
vic_int_t <- st_transform(vic_int, crs = 4326, "+proj=longlat +ellps=WGS84 +datum=WGS84")
st_crs(vic_int_t)
vic_int_t
vic_int_t$AAA <- vic_int_t$AAA %>% replace_na(0)
vic_int_w1_plot <- ggplot() + 
                  scale_fill_gradient2(name="Count of GPS points", low="lightblue", high = "darkblue") +
                  geom_sf(data = vic_int_t, aes(colour = AAA)) +
                  coord_sf(
                      xlim = sf::st_bbox(vic_int_t)[c(1,3)],
                      ylim = sf::st_bbox(vic_int_t)[c(2,4)]) + 
                  scale_color_manual(name="Infrastructure 2017", labels=c("Existing", "AAA"), values=c("grey80", "black")) +
                  annotation_scale() + 
                  theme_map()
plot(vic_int_w1_plot)
ggsave("vic_int_w1_plot.jpg", dpi = 150, height = 4, width = 6)
```

### Formatting and create buffer
```{r}
table(vic_int_t$AAA)
w1_intervention <- filter(vic_int_t, AAA == "V")

# convert pandora to sf
w1_intervention <- st_transform(w1_intervention, 26910)

# apply 50m, 70m, and 100m buffer
w1_intervention_buffer_70 = st_buffer(w1_intervention$geometry, dist = 70) 
w1_intervention_buffer_50 = st_buffer(w1_intervention$geometry, dist = 50) 
w1_intervention_buffer_100 = st_buffer(w1_intervention$geometry, dist = 100) 

plot(w1_intervention_buffer_70)
```

# Read in 2019 Shape file

```{r}
vic_int_2019 <- st_read("/Users/dfuller/Documents/INTERACT/data/intervention/victoria/IBIMS_2019.shp")
st_crs(vic_int_2019)
```

#### Plot Vic 2019 shape 
```{r}
vic_int_t2 <- st_transform(vic_int_2019, "+proj=longlat +ellps=WGS84 +datum=WGS84")
st_crs(vic_int_t2)
vic_int_t2
vic_int_t2$Notes <- vic_int_t2$Notes %>% replace_na(0)
vic_int_t2$AAA <- if_else(vic_int_t2$Notes == 0, 0, 1)
vic_int_t2$AAA <- as.factor(vic_int_t2$AAA)

vic_int_w2_plot <- ggplot() + 
                  scale_fill_gradient2(name="Count of GPS points", low="lightblue", high = "darkblue") +
                  geom_sf(data = vic_int_t2, aes(colour = AAA)) +
                  coord_sf(
                      xlim = sf::st_bbox(vic_int_t2)[c(1,3)],
                      ylim = sf::st_bbox(vic_int_t2)[c(2,4)]) + 
                  scale_color_manual(name="Infrastructure 2019", labels=c("Existing", "AAA"), values=c("grey80", "black")) +
                  annotation_scale() + 
                  theme_map()
plot(vic_int_w2_plot)
ggsave("vic_int_w2_plot.jpg", dpi = 150, height = 4, width = 6)
```

### Formatting and create buffer
```{r}
table(vic_int_t2$AAA)
w2_intervention <- filter(vic_int_t2, AAA == "1")

w2_intervention_1 <- st_combine(w2_intervention)
w2_intervention_1 <- st_as_sf(w2_intervention_1)
w2_intervention_1 <- st_transform(w2_intervention_1, 26910)

w2_intervention_buffer_70 = st_buffer(w2_intervention_1$x, dist = 70) # According to stack exchangers the distance is in meters
w2_intervention_buffer_50 = st_buffer(w2_intervention_1$x, dist = 50)
w2_intervention_buffer_100 = st_buffer(w2_intervention_1$x, dist = 100)

plot(w2_intervention_buffer_70)
```

# Get intersections of points in buffers for each wave

## Wave 1 2017

### Convert sd_data lat/long to polygon using st_as_sf

```{r}
SD_vic_one <- filter(sd_data, wave_id == 1)

SD_vic_one_sf <- st_as_sf(SD_vic_one, coords = c("lon", "lat"), crs = 4326)
```

### Run intersections code for bike_lanes_1 (pandora) and gps participants

```{r}
w1_intervention_buffer_70 <- st_transform(w1_intervention_buffer_70, 4326)
w1_intervention_buffer_70 <- st_as_sf(w1_intervention_buffer_70)

w1_intervention_buffer_50 <- st_transform(w1_intervention_buffer_50, 4326)
w1_intervention_buffer_50 <- st_as_sf(w1_intervention_buffer_50)

w1_intervention_buffer_100 <- st_transform(w1_intervention_buffer_100, 4326)
w1_intervention_buffer_100 <- st_as_sf(w1_intervention_buffer_100)

SD_vic_one_sf$exposed_70 <- ifelse(sf::st_intersects(SD_vic_one_sf, w1_intervention_buffer_70, sparse = F), 1, 0)
SD_vic_one_sf$exposed_50 <- ifelse(sf::st_intersects(SD_vic_one_sf, w1_intervention_buffer_50, sparse = F), 1, 0)
SD_vic_one_sf$exposed_100 <- ifelse(sf::st_intersects(SD_vic_one_sf, w1_intervention_buffer_100, sparse = F), 1, 0)

table(SD_vic_one_sf$exposed_70)
SD_vic_one$exposed_70 <- as.factor(SD_vic_one_sf$exposed_70)
SD_vic_one$exposed_50 <- as.factor(SD_vic_one_sf$exposed_50)
SD_vic_one$exposed_100 <- as.factor(SD_vic_one_sf$exposed_100)

ggplot() + 
        geom_sf() +
        geom_sf(data = w1_intervention_buffer_70) +                
        geom_point(aes(x = lon, y = lat, colour = exposed_70), data = SD_vic_one, alpha = 0.2) +
        geom_sf(data = w1_intervention_buffer_70) +
        annotation_scale() + 
        theme_map()
ggsave("exposed_2017.jpg", dpi = 150, height = 4, width = 6)
```

## Wave 2 2019

```{r}
SD_vic_two <- filter(sd_data, wave_id == 2)

SD_vic_two_sf <- st_as_sf(SD_vic_two, coords = c("lon", "lat"), crs = 4326)
```


```{r}
w2_intervention_buffer_70 <- st_transform(w2_intervention_buffer_70, 4326)
w2_intervention_buffer_70 <- st_as_sf(w2_intervention_buffer_70)

w2_intervention_buffer_50 <- st_transform(w2_intervention_buffer_50, 4326)
w2_intervention_buffer_50 <- st_as_sf(w2_intervention_buffer_50)

w2_intervention_buffer_100 <- st_transform(w2_intervention_buffer_100, 4326)
w2_intervention_buffer_100 <- st_as_sf(w2_intervention_buffer_100)

SD_vic_two_sf$exposed_70 <- ifelse(sf::st_intersects(SD_vic_two_sf, w2_intervention_buffer_70, sparse = F), 1, 0)
SD_vic_two_sf$exposed_50 <- ifelse(sf::st_intersects(SD_vic_two_sf, w2_intervention_buffer_50, sparse = F), 1, 0)
SD_vic_two_sf$exposed_100 <- ifelse(sf::st_intersects(SD_vic_two_sf, w2_intervention_buffer_100, sparse = F), 1, 0)

table(SD_vic_two_sf$exposed_70)
SD_vic_two$exposed_70 <- as.factor(SD_vic_two_sf$exposed_70)
SD_vic_two$exposed_50 <- as.factor(SD_vic_two_sf$exposed_50)
SD_vic_two$exposed_100 <- as.factor(SD_vic_two_sf$exposed_100)

ggplot() + 
        geom_sf() +
        geom_sf(data = w2_intervention_buffer_70) +                
        geom_point(aes(x = lon, y = lat, colour = exposed_70), data = SD_vic_two, alpha = 0.2) +
        geom_sf(data = w2_intervention_buffer_70) +
        annotation_scale() + 
        theme_map()
ggsave("exposed_2019.jpg", dpi = 150, height = 4, width = 6)
```

## Combining Exposure data from Wave 1 and Wave 2

```{r}
sd_data_exposure <- bind_rows(SD_vic_one, SD_vic_two)

table(sd_data_exposure$wave_id, sd_data_exposure$exposed_70)

write_csv(sd_data_exposure, "/Users/dfuller/Documents/INTERACT/data/sensors/sd_data_exposure.csv")
```
