---
title: "Buffer"
author: "Jonathan Slaney"
date: "23/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for master's thesis buffer calculation

## Required packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(naniar)
library(ggmap)
library(ggthemes)
library(sf)
library(rgeos)
library(cancensus)
library(cowplot)
library(ggspatial)
library(knitr)
```

## Game plan

1. Filter SD participants
2. Simplify date
3. Summarize (makes results table of MVPA)
4. Figures
5. Visualize GPS points + bike infrastructure 2017/ 2019
6. Apply 70m buffer

# Filter SD Participants
```{r}
## Reading in SD data
```{r}
SD_vic_one <- read_csv("~/INTERACT/SenseDoc/victoria_01_top_1min.csv") # read in SD w1 participants n = 129
SD_vic_one <- SD_vic_one %>% mutate(sensedoc = "1") # Add variable to SD w1 (1)
SD_vic_two <- read_csv("~/INTERACT/SenseDoc/victoria_02_top_1min.csv") # read in SD w2 participants n = 153
SD_vic_two <- SD_vic_two %>% mutate(sensedoc = "2") # Add variable to victoria health w1 (1)
SD_vic_all <- full_join(SD_vic_one, SD_vic_two)

tabyl(SD_vic_all$interact_id)
```

 
### Reading in the physical activity data from SenseDoc
```{r warning=FALSE}
data_temp <- NULL
data_temp <- dir(path = "/Users/dfuller/Documents/INTERACT/data/sensors/", full.names = TRUE, pattern = "*_sd.csv", recursive = TRUE) %>%
   purrr::map(function(i){
     dfhx <- read.csv(i, header = TRUE)
     temp <- bind_rows(data_temp, dfhx)
   })
sd_data <- bind_rows(data_temp)
rm(data_temp)
table(sd_data$city)
```

### Reading in the physical activity data from Ethica
```{r warning=FALSE}
data_temp <- NULL
data_temp <- dir(path = "/Users/dfuller/Documents/INTERACT/data/sensors/", full.names = TRUE, pattern = "*_ethica.csv", recursive = TRUE) %>%
   purrr::map(function(i){
     dfhx <- read.csv(i, header = TRUE)
     temp <- bind_rows(data_temp, dfhx)
   })
ethica_data <- bind_rows(data_temp)
rm(data_temp)
table(ethica_data$city)
```

## Some basic cleaning

```{r warning=FALSE}
# Filter out if they are not in the city, Reason: No CTUID for out of the city
sd_data <- sd_data %>% filter(in_city == 1 & wearing == 1)
sd_data <- sd_data %>%
	mutate(activity_levels = case_when(
		x_count < 100 ~ "sedentary",
		x_count >= 100 & x_count <= 1951 ~ "light",
		x_count >= 1951 & x_count <= 5724 ~ "moderate",
	  x_count >= 5725 ~ "vigorous"
	))
ethica_data <- ethica_data %>%
	mutate(activity_levels = case_when(
		x_count < 100 ~ "sedentary",
		x_count >= 100 & x_count <= 1951 ~ "light",
		x_count >= 1951 & x_count <= 5724 ~ "moderate",
	  x_count >= 5725 ~ "vigorous"
	))
```

## Create a date column and add a minutes in census tract by id, date, and census tract column 

```{r}
#### SenseDoc
table(sd_data$city_id)
sd_data$date <- sd_data$utcdate %>% as.Date()
sd_data$minutes <- 1
sd_data <- sd_data %>% 
  group_by(interact_id, date, city_id) %>% 
  mutate(
      minutes_id_date_city = sum(minutes)
  )
### Ethica
table(ethica_data$city_id)
ethica_data$date <- ethica_data$utcdate %>% as.Date()
ethica_data$minutes <- 1
ethica_data <- ethica_data %>% 
  group_by(interact_id, date, city_id) %>% 
  mutate(
      minutes_id_date_city = sum(minutes)
  )
```

### MPVA Minutes SenseDoc

```{r}
table(sd_data$activity_levels)
table(sd_data$wearing)
### MVPA Minutes
sd_data <- sd_data %>%
	mutate(mvpa = case_when(
		activity_levels == "light" ~ 0,
		activity_levels == "sedentary" ~ 0,
		activity_levels == "moderate" ~ 1,
		activity_levels == "vigorous" ~ 1
	))
### Sed Minutes
sd_data <- sd_data %>%
	mutate(sed = case_when(
		activity_levels == "light" ~ 0,
		activity_levels == "sedentary" ~ 1,
		activity_levels == "moderate" ~ 0,
		activity_levels == "vigorous" ~ 0
	))
### Sed Minutes
sd_data <- sd_data %>%
	mutate(light_pa = case_when(
		activity_levels == "light" ~ 1,
		activity_levels == "sedentary" ~ 0,
		activity_levels == "moderate" ~ 0,
		activity_levels == "vigorous" ~ 0
	))
sd_data <- sd_data %>% 
    group_by(interact_id, date, city_id) %>% 
      mutate(
        total_mvpa_minutes = sum(mvpa),
        total_sed_minutes = sum(sed),
        total_light_pa_minutes = sum(light_pa)
        )
sd_pa_table <- sd_data %>%
                group_by(interact_id, date, city_id) %>%
                  summarize(
                    time = mean(minutes_id_date_city, na.rm = TRUE),
                    wearing = mean(wearing, na.rm = TRUE),
                    mean_mpva_sd = mean(total_mvpa_minutes, na.rm = TRUE), 
                    sd_mpva_sd = sd(total_mvpa_minutes, na.rm = TRUE), 
                    mean_sed_sd = mean(total_sed_minutes, na.rm = TRUE), 
                    sd_sed_sd = sd(total_sed_minutes, na.rm = TRUE), 
                    mean_light_sd = mean(total_light_pa_minutes, na.rm = TRUE), 
                    sd_light_sd = sd(total_light_pa_minutes, na.rm = TRUE), 
                    na_count = sum(is.na(total_mvpa_minutes)), 
                    count = n()
                  )
sd_pa_table
sd_sum_table <- sd_pa_table %>%
                group_by(city_id) %>%
                  summarize(
                    time = mean(time, na.rm = TRUE), 
                    wearing = mean(wearing, na.rm = TRUE), 
                    mean_mpva_sd = mean(mean_mpva_sd, na.rm = TRUE), 
                    mean_sed_sd = mean(mean_sed_sd, na.rm = TRUE), 
                    mean_light_sd = mean(mean_light_sd, na.rm = TRUE), 
                    na_count = sum(is.na(time)), 
                    count = n()
                  )
sd_sum_table
```

### SD Activity Figures by city

```{r}
##  formula = y ~ s(x, bs = "cs") with method = "REML".
saskatoon_activity <-  sd_pa_table %>% 
              filter(city_id == "saskatoon") %>% 
              ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd),  colour = "black") +    
                  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                  ylim(0, 400) +
                  labs(x = "Date", y = "Minutes") +
                  theme_classic()
plot(saskatoon_activity)
ggsave("saskatoon_activity.jpg", dpi = 150, height = 4, width = 6)
```

```{r}
montreal_activity <-  sd_pa_table %>% 
              filter(city_id == "montreal") %>% 
              ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd), colour = "black") +    
                  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                  ylim(0, 400) +
                  labs(x = "Date", y = "Minutes") +
                  theme_classic()
plot(montreal_activity)
ggsave("montreal_activity.jpg", dpi = 150, height = 4, width = 6)
```

```{r}
vancouver_activity <-  sd_pa_table %>% 
              filter(city_id == "vancouver") %>% 
              ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd), colour = "black") +           
                  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                  ylim(0, 400) +
                  labs(x = "Date", y = "Minutes") +  
                  theme_classic()
plot(vancouver_activity)
ggsave("vancouver_activity.jpg", dpi = 150, height = 4, width = 6)
```

```{r}
victoria_activity <-  sd_pa_table %>% 
          filter(city_id == "victoria") %>% 
          ggplot() + 
                    geom_smooth(aes(x = date, y = mean_light_sd), colour = "black", linetype = "dashed") +
                    geom_smooth(aes(x = date, y = mean_mpva_sd), colour = "grey") + 
                    geom_smooth(aes(x = date, y = mean_sed_sd), colour = "black") +     
                scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
                ylim(0, 400) +
                labs(x = "Date", y = "Minutes") +
                theme_classic()
plot(victoria_activity)
ggsave("victoria_activity.jpg", dpi = 150, height = 4, width = 6)
```

# Interventions SenseDoc Data

### Victoria

```{r}
vic_cma <- get_census(dataset='CA16', regions=list(CMA="59935"),
                          level='CMA', use_cache = TRUE, geo_format = "sf")
vic_sd <- sd_data %>% filter(city_id == "victoria" & in_city == 1) 
sd_vic_days <- as.data.frame(unique(vic_sd$date))
vic_int <- st_read("/Users/dfuller/Documents/INTERACT/data/intervention/victoria/IBIMS_2017.shp")
st_crs(vic_int)
vic_int_t <- st_transform(vic_int, crs = 4326, "+proj=longlat +ellps=WGS84 +datum=WGS84")
st_crs(vic_int_t)
vic_int_t
vic_int_t$AAA <- vic_int_t$AAA %>% replace_na(0)
vic_int_plot <- ggplot() + 
                  geom_sf(data = vic_cma) +
                  geom_hex(aes(x = lon, y = lat), binwidth = c(0.005, 0.005), data = vic_sd, alpha = 0.8) +
                  scale_fill_gradient2(name="Count of GPS points", low="lightblue", high = "darkblue") +
                  geom_sf(data = vic_int_t, aes(colour = AAA)) +
                  coord_sf(
                      xlim = sf::st_bbox(vic_int_t)[c(1,3)],
                      ylim = sf::st_bbox(vic_int_t)[c(2,4)]) + 
                  scale_color_manual(name="Cycling Infrastructure", labels=c("Existing", "AAA"), values=c("grey80", "black")) +
                  annotation_scale() + 
                  theme_map()
plot(vic_int_plot)
ggsave("vic_int_plot.jpg", dpi = 150, height = 4, width = 6)
```

# GPS Maps

### Victoria

```{r}
### Full View
vic_basemap <- get_map(c(-123.5, 48.5),
                     source = "google",
                     maptype = "roadmap", crop = FALSE,
                     zoom = 10)
plot(vic_basemap)
vic_points <- ggmap(vic_basemap) + 
                  geom_bin2d(aes(x = lon, y = lat), binwidth = c(0.015, 0.015), data = vic_sd, alpha = 1) +
                  scale_fill_gradient2(low="darkred", high = "darkblue") +
                  theme_map()
plot(vic_points)
ggsave("vic_points.jpg", dpi = 150, height = 4, width = 6)
### Zoom 
vic_basemap_zoom <- get_map(location = "Victoria, BC, Canada",
                     source = "google",
                     maptype = "roadmap", crop = FALSE,
                     zoom = 13)
plot(vic_basemap_zoom)
vic_points_zoom <- ggmap(vic_basemap_zoom) + 
                  geom_bin2d(aes(x = lon, y = lat), binwidth = c(0.0025, 0.0025), data = vic_sd, alpha = 0.8) +
                  scale_fill_gradient2(high = "darkblue") +
                  theme_map()
plot(vic_points_zoom)
ggsave("vic_points_zoom.jpg", dpi = 150, height = 4, width = 6)
``` 

# Participant Data Flow

## Victoria

```{r}
## Veritas data VIC
veritas_vic <- read_csv("/Users/dfuller/Documents/INTERACT/data/veritas/veritas_1vic_main_1884baf.csv")
veritas_vic$veritas <- 1
### Health data 
data_small$health <- 1 
data_vic <- data_small %>%
              filter(city_id == "Victoria") %>%
              select(interact_id, city_id, health) 
length(data_vic$health) ### Number of Health Participants
flow_vic <- left_join(data_vic, veritas_vic)
table(flow_vic$veritas) ### Number of VERITAS Participants
### SenseDoc
vic_sd_small <- vic_sd %>%
                  group_by(interact_id) %>%
                  summarize(
                    interact_id = first(interact_id),
                    sensedoc = 1, 
                  )
flow_vic <- left_join(flow_vic, vic_sd_small)
table(flow_vic$sensedoc)  ### Number of SenseDoc Participants