---
title: "regression_analysis"
author: "Daniel Fuller"
date: "12/04/2021"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(lme4)
library(tidyverse)
library(gtools)
library(lubridate)
library(DRDID)
library(did)
library(modelsummary)
library(broom.mixed)
```


## Analysis plan

1. Descriptive statistics outcome and exposure
2. Merge in demographic and weather variables 
3. Regression outcome and exposure (as per change discussions)
4. Sensitivity analysis (exposure changes)

### Read in data

```{r}
data <- read_csv("/Users/dfuller/Documents/INTERACT/data/sensors/sd_data_exposure.csv")
```

## Demographic data and weather

### Merging demographics

```{r}
health_data <- read_csv("/Users/dfuller/Documents/INTERACT/data/health_clean.csv")

health_data <- health_data %>%
                  select(education_recode, gender_recode2, income_recode, age_recode, white, asian, indigenous, black, latin_american, 
                         middle_eastern, other_ethnicity, interact_id)

data <- left_join(data, health_data, by = c("interact_id"))
```

### Merging weather

```{r}
weather_data <- read_csv("/Users/dfuller/Documents/INTERACT/data/weather/2016_2020_weather_vic_van_sask_mtl.csv")

weather_data <- weather_data %>% dplyr::select(date_time, city_id, max_temp_c, min_temp_c, mean_temp_c, total_rain_mm, total_snow_mm, total_precip_mm, snow_ground_cm, speed_gust_km_h)

weather_data$date <- ymd(weather_data$date_time)

weather_data <- weather_data %>% filter(city_id == "Victoria")

weather_data <- arrange(weather_data, date)
data <- arrange(data, date)

data <- left_join(data, weather_data, by = c("date"))
```

### Exposure over time 

```{r}
## Overall 
table(data$wave_id, data$exposed_70)

## Individual level
data_exposure <- data %>%
                  group_by(interact_id, wave_id, date) %>%
                    summarise(
                      sum_exp_70 = sum(exposed_70), 
                      sum_exp_50 = sum(exposed_50), 
                      sum_exp_100 = sum(exposed_100), 
                      mvpa = first(total_mvpa_minutes),
                      sed = first(total_sed_minutes),
                      light = first(total_light_pa_minutes),
                      rel_exp_70 = sum(exposed_70)/n(),
                      rel_exp_50 = sum(exposed_50)/n(),
                      rel_exp_100 = sum(exposed_100)/n(),
                      minutes = first(minutes_id_date),
                      mean_temp_c = first(mean_temp_c),
                      total_precip_mm = first(total_precip_mm),
                      snow_ground_cm = first(snow_ground_cm),
                      speed_gust_km_h = first(speed_gust_km_h),
                      education_recode = first(education_recode),
                      gender_recode2 = first(gender_recode2),
                      income_recode = first(income_recode),
                      age_recode = first(age_recode),
                      white = first(white),
                      asian = first(asian),
                      indigenous = first(indigenous),
                      black = first(black),
                      latin_american = first(latin_american),
                      middle_eastern = first(middle_eastern),
                      other_ethnicity - first(other_ethnicity)
                    )

data_exposure$date_time <- as.factor(data_exposure$date)

data_exposure$speed_gust_km_h <- as.numeric(data_exposure$speed_gust_km_h)
```

### Histograms of absolute exposure (Total number of minutes)

```{r}
summary(data_exposure$sum_exp_70)

### Removing participants with more than 500 minutes of exposure
data_exposure$sum_exp_70 <- if_else(data_exposure$sum_exp_70 > 500, NA_real_, data_exposure$sum_exp_70)
data_exposure$sum_exp_50 <- if_else(data_exposure$sum_exp_50 > 500, NA_real_, data_exposure$sum_exp_50)
data_exposure$sum_exp_100 <- if_else(data_exposure$sum_exp_100 > 500, NA_real_, data_exposure$sum_exp_100)

data_exposure <- data_exposure %>% 
                    mutate(
                      sum_exp_70_quint = ntile(sum_exp_70, 5),
                      sum_exp_50_quint = ntile(sum_exp_50, 5),
                      sum_exp_100_quint = ntile(sum_exp_100, 5)
                      )

data_exposure$sum_exp_70_quint <- as.factor(data_exposure$sum_exp_70_quint)
data_exposure$sum_exp_50_quint <- as.factor(data_exposure$sum_exp_50_quint)
data_exposure$sum_exp_100_quint <- as.factor(data_exposure$sum_exp_100_quint)

table(data_exposure$sum_exp_70_quint)
table(data_exposure$sum_exp_100_quint)

```

```{r}
abs_exposure_histo <- ggplot(data_exposure, aes(sum_exp_70)) + 
  geom_histogram() + 
  facet_wrap(~ wave_id) + 
  theme_classic()

plot(abs_exposure_histo)
```

### Histograms of relative exposure (% of total minutes exposed)

```{r}
summary(data_exposure$rel_exp_70)

### Removing participants with more than 40% exposure
data_exposure$rel_exp_70 <- if_else(data_exposure$rel_exp_70 > 0.40, NA_real_, data_exposure$rel_exp_70)
data_exposure$rel_exp_50 <- if_else(data_exposure$rel_exp_50 > 0.40, NA_real_, data_exposure$rel_exp_50)
data_exposure$rel_exp_100 <- if_else(data_exposure$rel_exp_100 > 0.40, NA_real_, data_exposure$rel_exp_100)

data_exposure <- data_exposure %>% 
                    mutate(
                      rel_exp_70_quint = ntile(rel_exp_70, 5),
                      rel_exp_50_quint = ntile(rel_exp_50, 5),
                      rel_exp_100_quint = ntile(rel_exp_100, 5)
                      )
data_exposure$rel_exp_70_quint <- as.factor(data_exposure$rel_exp_70_quint)
data_exposure$rel_exp_50_quint <- as.factor(data_exposure$rel_exp_50_quint)
data_exposure$rel_exp_100_quint <- as.factor(data_exposure$rel_exp_100_quint)

table(data_exposure$rel_exp_70_quint)
table(data_exposure$rel_exp_100_quint)

```

```{r}
rel_exposure_histo <- ggplot(data_exposure, aes(rel_exp_70)) + 
  geom_histogram() + 
  facet_wrap(~ wave_id) + 
  theme_classic()

plot(rel_exposure_histo)
```

### Histograms of Moderate to vigorous PA 

```{r}
pa_histo <- ggplot(data_exposure, aes(mvpa)) + 
  geom_histogram() + 
  facet_wrap(~ wave_id) + 
  theme_classic()

plot(pa_histo)
```

### Scatterplot Absolute Exposure and Moderate to vigorous PA 

```{r}
abs_exp_pa_scatter <- ggplot(data_exposure, aes(x = sum_exp_70, y = mvpa)) + 
  geom_point(alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ wave_id) + 
  theme_classic()

plot(abs_exp_pa_scatter)
```

### Scatterplot Relative Exposure and Moderate to vigorous PA 

```{r}
rel_exp_pa_scatter <- ggplot(data_exposure, aes(x = rel_exp_70, y = mvpa)) + 
  geom_point(alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ wave_id) + 
  theme_classic()

plot(rel_exp_pa_scatter)
```

### Linear regression

```{r}
lm_models <- list(
  "Absolute Exposure" = lm(mvpa ~ sum_exp_70*factor(wave_id), data = data_exposure),
  "Relative Exposure" = lm(mvpa ~ rel_exp_70*factor(wave_id), data = data_exposure)
)

modelsummary(lm_models, fmt = "%.2f", statistic = 'conf.int')
```

## Multilevel models 

MLM models with person level random intercepts using the lmer package

### Absolute exposure with a 70 meter buffer and no covariates

```{r}
### Null Model
lmer_null_exp70_ln <- lmer(mvpa ~ 1 + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_null_exp70_ln)
broom.mixed::glance(lmer_null_exp70_ln)
```

```{r}
### Absolute Model Continuous
lmer_abs_exp70_ln <- lmer(mvpa ~ sum_exp_70*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp70_ln)
broom.mixed::glance(lmer_abs_exp70_ln)

### Absolute Model Quintiles
lmer_abs_exp70_q <- lmer(mvpa ~ sum_exp_70_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp70_q)
broom.mixed::glance(lmer_abs_exp70_q)
```

### Absolute exposure with a 70 meter buffer and covariates
```{r}
### Absolute Model Continuous
lmer_abs_exp70_ln_cov <- lmer(mvpa ~ sum_exp_70*factor(wave_id) + mean_temp_c + total_precip_mm + speed_gust_km_h + gender_recode2 + income_recode + age_recode + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp70_ln_cov)
broom.mixed::glance(lmer_abs_exp70_ln_cov)

### Absolute Model Quintiles
lmer_abs_exp70_q_cov <- lmer(mvpa ~ sum_exp_70_quint*factor(wave_id) + mean_temp_c + total_precip_mm + speed_gust_km_h + gender_recode2 + income_recode + age_recode + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp70_q_cov)
broom.mixed::glance(lmer_abs_exp70_q_cov)
```

## Relative Exposure

### Relative exposure with a 70 meter buffer and no covariates

```{r}
### Linear exposure
lmer_rel_exp_ln <- lmer(mvpa ~ rel_exp_70*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp_ln)

### Quintiles of exposure
lmer_rel_exp_q <- lmer(mvpa ~ rel_exp_70_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp_q)
```

### Relative exposure with a 70 meter buffer and covariates

```{r}
### Linear exposure
lmer_rel_exp_ln_cov <- lmer(mvpa ~ rel_exp_70*factor(wave_id) + mean_temp_c + total_precip_mm + speed_gust_km_h + gender_recode2 + income_recode + age_recode + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp_ln_cov)

### Quintiles of exposure
lmer_rel_exp_q_cov <- lmer(mvpa ~ rel_exp_70_quint*factor(wave_id) + mean_temp_c + total_precip_mm + speed_gust_km_h + gender_recode2 + income_recode + age_recode + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp_q_cov)
```

# Sensitivity Analysis for different buffers

## 50 Meter Buffer

Absolute Exposure 

```{r}
### Absolute Model Continuous
lmer_abs_exp50_ln <- lmer(mvpa ~ sum_exp_50*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp50_ln)

### Absolute Model Quintiles
lmer_abs_exp50_q <- lmer(mvpa ~ sum_exp_50_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp50_q)
```

### Relative Exposure

```{r}
### Linear exposure
lmer_rel_exp50_ln <- lmer(mvpa ~ rel_exp_50*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp50_ln)

### Quintiles of exposure
lmer_rel_exp50_q <- lmer(mvpa ~ rel_exp_50_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp50_q)
```

## 100 Meter Buffer

Absolute Exposure 

```{r}
### Absolute Model Continuous
lmer_abs_exp100_ln <- lmer(mvpa ~ sum_exp_100*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp100_ln)

### Absolute Model Quintiles
lmer_abs_exp100_q <- lmer(mvpa ~ sum_exp_100_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_abs_exp100_q)
```

### Relative Exposure

```{r}
### Linear exposure
lmer_rel_exp100_ln <- lmer(mvpa ~ rel_exp_100*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp100_ln)

### Quintiles of exposure
lmer_rel_exp100_q <- lmer(mvpa ~ rel_exp_100_quint*factor(wave_id) + (1 | date_time) + (1 | interact_id), data = data_exposure)
summary(lmer_rel_exp100_q)
```
